An introduction to wavelets using R

### 2024-08-08 text/pending/wavelets.Rmd
Updated references-from-jsm-2024

---
title: "An introduction to wavelets using R"
author: "Steve Simon"
source: "http://www.pmean.com/wavelets.html"
date: "2014-01-01"
category: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: partial
---

>>>>

---
title: "An introduction to wavelets using R"
author: "Steve Simon"
source: "http://www.pmean.com/wavelets.html"
date: "2014-01-01"
categories: 
- Blog post
tags:
- Checking assumptions  
- Linear regression
- R software
- Rmarkdown graphs
output: html_document
page_update: partial
---
